Robust DPG stability II

### 2012-04-05 docs/NewBCRobustness_paper/paper.tex
changing bib and tex of paper.  adding new sections on explaining robustness
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@446 36274a68-8941-4c93-80ef-affaed5139da

The finite element/Galerkin method has been widely utilized in engineering to solve partial differential equations related to simulation of solid mechanics problems. For many problems in engineering, the bilinear forms resulting from these partial differential equations are symmetric and coercive (positive-definite), and it is well known that the finite element method produces near-optimal results for such problems. However, standard Bubnov-Galerkin methods tend to perform poorly for the class of partial-differential equations known as singularly perturbed problems. Singularly perturbed problems are problems where a given parameter may be either very small or very large in the context of physical problems.  An additional complication of singularly perturbed problems is that very often, in the limiting case of the parameter blowing up or decreasing to zero, the partial differential equation itself will change form. A canonical example is the convection-diffusion equation with Dirichlet boundary conditions. In 1D, this equation is
\begin{align*}
u'-\epsilon u'' &= f
\end{align*}
The equation represents the change in the concentration of some quantity $u$ in some medium from both convective and diffusive effects. The parameter $\epsilon$ represents the diffusivity, and in the limit of an inviscid medium as $\epsilon\rightarrow 0$, the partial differential equation changes types, going from a parabolic to a hyperbolic equation. For Dirichlet boundary conditions $u(0)=u_0$ and $u(1)= u_1$, the solution can develop sharp boundary layers of order $\epsilon$ near the outflow.

The finite element method has notoriously performed poorly for both this example, and for many other singularly perturbed problems. This poor performance is captured by the error bound for the finite element method applied to convection-diffusion equations
\[
\|u-u_h\|_E \leq C(\epsilon) \inf_{w_h}\|u-w_h\|_U,
\]
where $C(\epsilon)$ grows as $\epsilon$ approaches its limiting case. The growth of $C$ with $\epsilon$ is referred to as a \textit{loss of robustness} in $\epsilon$, where the bound on the error in the finite element solution by the best approximation error increases as $\epsilon\rightarrow 0$.  Intuitively, as our singular perturbation parameter changes, our finite element error is bounded more and more loosely by the best approximation error, allowing for more and more error in the finite element solution for as $\epsilon$ shrinks. The manifestation of this loss of robustness in the finite element solution of the 1D convection-diffusion problem is the growth of spurious oscillations as $\epsilon\rightarrow 0$.  For a coarse mesh and small values of $\epsilon$, the Galerkin approximation of the solution to the convection-diffusion equation develops oscillations of magnitude $O(\epsilon^{-1})$.

@@

@@

The discontinuous Petrov-Galerkin (DPG) method is the pairing of the concept of locally computable optimal test functions with the so-called ``ultra-weak formulation". For a given operator equation in strong form $Au = f$, the ultra-weak formulation is
\[
b\left(\left(\widehat{u},u\right),v\right) - l(v) = \langle \widehat{u}, [v] \rangle - (u,A^*v) - (f,v) = 0
\]
where $A^*$ is the formal adjoint resulting from integration by parts,
and $[v]$ is the jump of the test function $v$ across element
boundaries.  Both the inner product and formal adjoint are understood
in an element-wise fashion. Under the ultra-weak formulation, the
regularity requirement on each solution variable is relaxed through
integration by parts.  Moreover, to maintain conformity while seeking
an $L^2$ setting on interior ``field" variables, boundary terms are
identified as additional new unknowns.  The result is a hybridized DG \textcolor{blue}{TB: This is not true, the hybridized DG method does not hybridize both traces/fluxes}
method with locally supported optimal test functions, with energy
setting
\begin{align*}
u&\in L^2(\Omega)\\
v&\in V=D(A^*) \\
\widehat{u}&\in T(D(A))
\end{align*}
where $D(A^*)$ is the domain of the formal adjoint $A^*$, and $T(D(A))$ is the trace space of the domain of the operator $A$ in its strong form. A more comprehensive discussion of the abstract setting of DPG, as well as a proof of well-posedness, is developed using the graph norm in \cite{DPGFriedrichs}.

@@

Our aim now is to translate the above abstract language to a concrete model problem in computational fluid dynamics.  We consider the model convection-diffusion problem on domain $\Omega \in \mathbb{R}^d$ with boundary $\Gamma$
\begin{align}
\div (\beta u) - \epsilon\Delta v &= f  \label{primal}
\end{align}
in first order form
\begin{align*}
\div (\beta u - \sigma) &= f  \\
\frac{1}{\epsilon}\sigma - \grad u &= 0
\end{align*}
with the corresponding variational form (prior to the application of boundary conditions)
\begin{align*}
b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle + \langle \widehat{f}_n, \left[v\right] \rangle 
\end{align*}
where $\left[ \tau_n \right]$ and $\left[ v\right]$ denote the jumps in $\tau_n$ and $v$ across an element edge, defined as
\begin{align*}
\left[ \tau_n \right] &= \tau^+ \cdot n^+ + \tau^-\cdot n^-\\
\left[ v\right] &= v^+{\rm sgn}(n^+) + v^-{\rm sgn}(n^-)
\end{align*}
where $n$ is the outward normal vector to an element edge, and ${\rm sgn}(n)$ is 1 if $n$ aligns with a given global orientation, and $-1$ otherwise. \textcolor{red}{I need to find more simple way to explain sgn} \textcolor{blue}{TB: see my DPG Friedrichs paper for the explanation}.

@@

Finally, we split the boundary $\Gamma$ into three portions
\begin{align*}
\Gamma_{-} &\coloneqq \{x\in \Gamma; \beta_n(x) < 0\} \quad {\rm (inflow)}\\
\Gamma_{+} &\coloneqq \{x\in \Gamma; \beta_n(x) > 0\} \quad {\rm (outflow)}\\
\Gamma_{0} &\coloneqq \{x\in \Gamma; \beta_n(x) = 0\}
\end{align*}
We adopt a new inflow boundary condition, given by Hesthaven et al in \cite{Hesthaven96astable}, where we set
\[
\beta_n u - \sigma_n = f_n = u_0
\]
on $\Gamma_-$, and continue \textcolar{blue}{TB: from where?} with the
wall boundary condition $u=0$ on $\Gamma_+$.  For our model problem,
as for many problems of interest in computational fluid dynamics, we
expect $\grad u$ to be small near the inflow, and that the solutions
to \eqref{primal} using $\beta_n u - \sigma_n = f_n = u_0$ on $\Gamma_-$
will converge to that using $u=u_0$ on $\Gamma_-$  for sufficiently small $\epsilon$.
Under these new boundary conditions, our variational problem $b(u,v) =
l(v)$ is now defined by
\begin{align*}
b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right),
\left(\tau, v\right)\right) &= \left(u,\div \tau - \beta \cdot \grad
v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle
\left[\tau_n\right], \widehat{u} \rangle_{\Gamma_-\cup \Gamma_h^0} +
\langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_+ \cup
  \Gamma_h^0} \\ l\left(\left(\tau,v\right)\right) &= \left(f,
v\right) %+ \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_+}
- \langle u_0, v \rangle_{\Gamma_-}
\end{align*}

@@

\subsection{Approximability of the quasi-optimal test norm}
\textcolor{blue}{need to define what we mean by robustness. perharps the best place is in the introduction}

For convection-diffusion, the quasi-optimal test norm is 
\[
\|\left(\tau, v\right)\|_V^2 = \| \div \tau - \beta \cdot \grad v
\|_{L^2}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2}^2 +
C_1\|v\|_{L^2}^2 + C_2\|\tau\|_{L^2}^2
\]
for some choice of constants $C_1$ and $C_2$.  
%We note that the optimal test norm will automatically guarantee the
%robust bound $\|\left(\tau, v\right)\|_V \leq \|u\|_{L^2}$.
However, use of this norm for the convection-diffusion problem is
difficult - the variational problem for optimal test functions using
the quasi-optimal test norm is equivalent to a reaction-diffusion
system \cite{DBLP:journals/procedia/NiemiCC11}.  Such systems also
develop strong boundary layers for small diffusion, and transforming
the problem to the reference element reveals that the inversion of the
inner product associated with the optimal test norm will induce strong
boundary layers of width $\epsilon/h^2$ in the optimal test functions.
In comparison, the quasi-optimal norm has yielded fantastic
\textcolor{blue}{we don't use fantastic in technical English, replace
  it with excellent, for example} results for the Helmholtz equation
and other wave propagation problems. The difference between the two
problems lies in the fact that, for wave propagation problems, the
mesh size tends to be on the order of the wavenumber $k$/singular
perturbation parameter. Transforming the variational problem using the
quasi-optimal test norm for wave propagation yields smooth optimal
test functions that are much easier to approximate over the reference
element. Typically, the wavenumbers $k$ of physical interest are
$O(100)-O(1000)$ with respect to a unit domain. The corresponding
finite element problems will typically be solved on meshes containing
approximately $O(k^d)$ elements in $\mathbb{R}^d$, well within the
range of a computationally tractable simulation. However, for
convection diffusion problems, the relevant range of $\epsilon$ for
physical problems can be as small as $1e-7$. Solving on partially
under-resolved meshes is thus unavoidable, and the approximability of
the optimal test functions must be addressed in order to take
advantage of the properties of DPG.

@@

Resolving such boundary layers present in quasi-optimal test functions
has been investigated numerically using specially designed (Shishkin)
subgrid meshes by Niemi, Collier, and Calo in
\cite{DBLP:journals/procedia/NiemiCC11}.  However, even with Shishkin
meshes, the approximation of optimal test functions under the
quasi-optimal norm is difficult and far more expensive and complex to
implement than approximation of test functions using a simple
$p$-enriched space for $V$. We approach this from a different
perspective, looking instead for robust test norms which do not induce
boundary layers in the approximation of optimal test functions, and do
so by formulating a general approach to analyzing the behavior of DPG
under a given test norm.

@@

\section{Strategy for proving robustness under a given test norm}

The main goal of this paper is to derive a test norm that \textit{does not induce boundary layers in the optimal test functions}, but still induces an energy norm \textit{that does not lose robustness as $\epsilon \rightarrow 0$}.  
%The first condition is satisfied by first decoupling norms on $\left(\tau,v\right)$ such that
%\[
%\left\|\left(\tau,v\right)\right\|_V = \|\tau\|_{H({\rm div},\Omega_h)} +  \|v\|_{H^1(\Omega_h)}.
%\]
%where $\|\tau\|_{H({\rm div},\Omega_h)}$ and $ \|v\|_{H^1(\Omega_h)}$ are both constructed as the sum of norm and seminorms on each respective space.  Ensuring that each seminorm/normed term is of the same order will allow for smooth solutions (under some assumptions on $\beta$).  
The avoidance of boundary layers in the test norm will be described in more detail in the section detailing numerical experiments. We focus first on quantifying the condition on robustness. Such a condition is equivalent to showing the robust boundedness of the energy error from above and below by norms on $U$ 
\[
\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim  \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2}
\]
\textcolor{blue}{As a reader, up to this point, I don't understand what robustness means and why the above double inequalities is the condition for robustness?}
where $\lesssim$ denotes a bound by a constant that will not grow as $\epsilon \rightarrow 0$. %The robust bound on the error in $\|\cdot\|_E$ from below by error in $\|\cdot\|_{U,1}$ is crucial to avoiding the instabilities associated with loss of robustness - 
\textcolor{red}{Explain in intuitive terms what the bounds above and below mean.}
Our goal is to explicitly derive the norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ that characterize this relation, taking into account the limiting case of $\epsilon \rightarrow 0$.

Our strategy for doing so is broken down into three parts.

@@

A second, weaker result is an upper bound on the energy norm
\[
\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-\left(u_h,\sigma_h,\widehat{u}_h,\widehat{f}_{n,h}\right)\right\|_{E} \lesssim \inf_{w\in U_h}\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-w_h\right\|_{U,2}
\]
where $\|\cdot \|_{U,2}$ is defined as
\[
\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,2}^2 \coloneqq \|u\|^2 + \frac{1}{\sqrt{\epsilon}}\left(\|\sigma\|^2 + \|\widehat{u}\|^2+ \|\widehat{f}_n\|^2\right).
\]
While the upper bound is robust, we have derived such a bound only by explicitly accounting for a factor of $\epsilon^{-1/2}$ in the bounding norm $\|\cdot \|_{U,2}$.  This implies that for very small $\epsilon$, the $L^2$ error may be much smaller than the energy error (in this sense, DPG may lose some efficiency for small $\epsilon$, though it is still guaranteed against losing robustness and stability). However, numerical experiments demonstrate much better results, and suggest that, at least for our example problems, $\|u-u_h\|_E \sim \|u-u_h\|_{U}$, implying that the induced energy norm may be equivalent to a norm on the group variable $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)$ that does not grow with $\epsilon$.

>>>>

The finite element/Galerkin method has been widely utilized in engineering to solve partial differential equations related to simulation of solid mechanics problems. For many problems in engineering, the bilinear forms resulting from these partial differential equations are symmetric and coercive (positive-definite), and it is well known that the finite element method produces near-optimal results for such problems. However, standard Bubnov-Galerkin methods tend to perform poorly for the class of partial-differential equations known as singularly perturbed problems. Singularly perturbed problems are problems where a given parameter may be either very small or very large in the context of physical problems.  An additional complication of singularly perturbed problems is that very often, in the limiting case of the parameter blowing up or decreasing to zero, the partial differential equation itself will change types (i.e from parabolic to hyperbolic). A canonical example is the convection-diffusion equation with Dirichlet boundary conditions.

\subsubsection{Convection-diffusion}

In 1D, the convection-diffusion equation is
\begin{align*}
u'-\epsilon u'' &= f
\end{align*}
The equation represents the change in the concentration of some quantity $u$ in some medium from both convective and diffusive effects. The parameter $\epsilon$ represents the diffusivity, and in the limit of an inviscid medium as $\epsilon\rightarrow 0$, the partial differential equation changes types, going from a parabolic to a hyperbolic equation. For Dirichlet boundary conditions $u(0)=u_0$ and $u(1)= u_1$, the solution can develop sharp boundary layers of order $\epsilon$ near the outflow.

The finite element method has notoriously performed poorly for both this example, and for many other singularly perturbed problems. This poor performance is captured by the error bound for the finite element method applied to convection-diffusion equations - for the standard Bubnov-Galerkin method with $u\in H^1(0,1)$, we have the bound given in \cite{roos2008robust}
\[
\|u-u_h\|_\epsilon \leq C \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
\]
for $C$ independent of $\epsilon$, and for $\|u\|_\epsilon \coloneqq \|u\|_{L^2} + \epsilon \|u'\|_{L^2}$. An alternative formulation of the above bound is 
\[
\|u-u_h\|_{H^1(0,1)} \leq C(\epsilon) \inf_{w_h}\|u-w_h\|_{H^1(0,1)},
\]
where $C(\epsilon)$ grows as $\epsilon\rightarrow 0$.

The dependence on $\epsilon$ in the bound of our finite element error by best approximation error is referred to as a \textit{loss of robustness}.  As our singular perturbation parameter changes, our finite element error is bounded more and more loosely by the best approximation error, allowing for more and more error in the finite element solution for as $\epsilon$ shrinks.

Intuitively, a non-robustness method will perform increasingly worse as $\epsilon$ decreases, independently of the best approximation error. For example, for a coarse mesh and small values of $\epsilon$, the Galerkin approximation of the solution to the convection-diffusion equation with a boundary layer develops spurious oscillations of magnitude $O(\epsilon^{-1})$ everywhere in the domain, even where best approximation error is small.

\subsubsection{Wave propagation}

@@

\subsubsection{Stabilization terms}

@@

The discontinuous Petrov-Galerkin (DPG) method is the pairing of the concept of locally computable optimal test functions with the so-called ``ultra-weak formulation". For a given operator equation in strong form $Au = f$, the ultra-weak formulation is
\[
b\left(\left(\widehat{u},u\right),v\right) - l(v) = \langle \widehat{u}, [v] \rangle - (u,A^*v) - (f,v) = 0
\]
where $A^*$ is the formal adjoint resulting from integration by parts,
and $[v]$ is the jump of the test function $v$ across element
boundaries.  Both the inner product and formal adjoint are understood
in an element-wise fashion. Under the ultra-weak formulation, the
regularity requirement on each solution variable is relaxed through
integration by parts.  Moreover, to maintain conformity while seeking
an $L^2$ setting on interior ``field" variables, boundary terms are
identified as additional new unknowns.  The result is a DG
method with locally supported optimal test functions, where both fluxes and traces are hybridized.  The energy setting is
\begin{align*}
u&\in L^2(\Omega)\\
v&\in V=D(A^*) \\
\widehat{u}&\in T(D(A))
\end{align*}
where $D(A^*)$ is the domain of the formal adjoint $A^*$, and $T(D(A))$ is the trace space of the domain of the operator $A$ in its strong form. A more comprehensive discussion of the abstract setting of DPG, as well as a proof of well-posedness, is developed using the graph norm in \cite{DPGFriedrichs}.

@@

Our aim now is to translate the above abstract language to a concrete model problem in computational fluid dynamics.  We consider the model convection-diffusion problem on domain $\Omega \in \mathbb{R}^d$ with boundary $\Gamma$
\begin{align}
\div (\beta u) - \epsilon\Delta v &= f  \label{primal}
\end{align}
in first order form
\begin{align*}
\div (\beta u - \sigma) &= f  \\
\frac{1}{\epsilon}\sigma - \grad u &= 0
\end{align*}
with the corresponding variational form (prior to the application of boundary conditions)
\begin{align*}
b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle + \langle \widehat{f}_n, \left[v\right] \rangle 
\end{align*}
where $\left[ \tau_n \right]$ and $\left[ v\right]$ denote the jumps in $\tau_n$ and $v$ across an element edge, defined as
\begin{align*}
\left[ \tau_n \right] &= \tau^+ \cdot n^+ + \tau^-\cdot n^-\\
\left[ v\right] &= v^+{\rm sgn}(n^+) + v^-{\rm sgn}(n^-)
\end{align*}
where $n$ is the outward normal vector to an element edge, and ${\rm sgn}(n)$ is 1 if $n$ aligns with a given normal orientation $n_e$ on each edge, and $-1$ otherwise (see Examples in \cite{DPGFriedrichs} for a more detailed explanation).

@@

Finally, we split the boundary $\Gamma$ into three portions
\begin{align*}
\Gamma_{-} &\coloneqq \{x\in \Gamma; \beta_n(x) < 0\} \quad {\rm (inflow)}\\
\Gamma_{+} &\coloneqq \{x\in \Gamma; \beta_n(x) > 0\} \quad {\rm (outflow)}\\
\Gamma_{0} &\coloneqq \{x\in \Gamma; \beta_n(x) = 0\}
\end{align*}
We adopt a new inflow boundary condition, given by Hesthaven et al in \cite{Hesthaven96astable}, where we set
\[
\beta_n u - \sigma_n = f_n = u_0
\]
on $\Gamma_-$, and use the standard wall boundary condition $u=0$ on $\Gamma_+$.  For our model problem,
as for many problems of interest in computational fluid dynamics, we
expect $\grad u$ to be small near the inflow, and that the solutions
to \eqref{primal} using $\beta_n u - \sigma_n = f_n = u_0$ on $\Gamma_-$
will converge to that using $u=u_0$ on $\Gamma_-$  for sufficiently small $\epsilon$.
Under these new boundary conditions, our variational problem $b(u,v) =
l(v)$ is now defined by
\begin{align*}
b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right),
\left(\tau, v\right)\right) &= \left(u,\div \tau - \beta \cdot \grad
v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle
\left[\tau_n\right], \widehat{u} \rangle_{\Gamma_-\cup \Gamma_h^0} +
\langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_+ \cup
  \Gamma_h^0} \\ l\left(\left(\tau,v\right)\right) &= \left(f,
v\right) %+ \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_+}
- \langle u_0, v \rangle_{\Gamma_-}
\end{align*}

@@

\subsection{Approximability of the quasi-optimal test norm}
%\textcolor{blue}{need to define what we mean by robustness. perharps the best place is in the introduction}

An ideal choice for the test norm would be the quasi-optimal norm; however, the form of the optimal test norm for convection-diffusion problems turns out to be quite problematic in the small diffusion limit.

For convection-diffusion, the quasi-optimal test norm is 
\[
\|\left(\tau, v\right)\|_V^2 = \| \div \tau - \beta \cdot \grad v
\|_{L^2}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2}^2 +
C_1\|v\|_{L^2}^2 + C_2\|\tau\|_{L^2}^2
\]
for some choice of constants $C_1$ and $C_2$.  
%We note that the optimal test norm will automatically guarantee the
%robust bound $\|\left(\tau, v\right)\|_V \leq \|u\|_{L^2}$.
However, use of this norm for the convection-diffusion problem is
difficult - the variational problem for optimal test functions using
the quasi-optimal test norm is equivalent to a reaction-diffusion
system \cite{DBLP:journals/procedia/NiemiCC11}.  Such systems also
develop strong boundary layers for small diffusion, and transforming
the problem to the reference element reveals that the inversion of the
inner product associated with the optimal test norm will induce strong
boundary layers of width $\epsilon/h^2$ in the optimal test functions.
In comparison, the quasi-optimal norm has yielded excellent results for the Helmholtz equation
and other wave propagation problems. The difference between the two
problems lies in the fact that, for wave propagation problems, the
mesh size tends to be on the order of the wavenumber $k$/singular
perturbation parameter. Transforming the variational problem using the
quasi-optimal test norm for wave propagation yields smooth optimal
test functions that are much easier to approximate over the reference
element. Typically, the wavenumbers $k$ of physical interest are
$O(100)-O(1000)$ with respect to a unit domain. The corresponding
finite element problems will typically be solved on meshes containing
approximately $O(k^d)$ elements in $\mathbb{R}^d$, well within the
range of a computationally tractable simulation. However, for
convection diffusion problems, the relevant range of $\epsilon$ for
physical problems can be as small as $1e-7$. Solving on partially
under-resolved meshes is thus unavoidable, and the approximability of
the optimal test functions must be addressed in order to take
advantage of the properties of DPG.

@@

Resolving such boundary layers present in quasi-optimal test functions
has been investigated numerically using specially designed (Shishkin)
subgrid meshes by Niemi, Collier, and Calo in
\cite{DBLP:journals/procedia/NiemiCC11}.  However, even with Shishkin
meshes, the approximation of optimal test functions under the
quasi-optimal norm is difficult and far more expensive and complex to
implement than approximation of test functions using a simple
$p$-enriched space for $V$. We approach this from a different
perspective, aiming instead to design a test norm that does not induce boundary layers, yet still maintains what we will define as \textit{robustness} - approximation properties that do not change over a range of $\epsilon$.

\subsection{Alternatives to the quasi-optimal test norm}

We expect the quasi-optimal test norm to deliver results that are close to the optimal test norm; namely, that the DPG finite element solution minimizes error a norm equivalent to
\[
\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U = \|u\|_{L^2(\Omega_h)} + \|\sigma\|_{L^2(\Omega_h)} +
\|\widehat{u}\| + \|\widehat{f}_n\|.
\]
This is an example of a \textit{robust} error bound - under the optimal test norm, we will return the best approximation error in the same norm \textit{independently} of $\epsilon$.  The precise definition of robustness for singularly perturbed problems can be given as follows - for a problem with singular perturbation parameter $\epsilon\rightarrow 0$ and exact solution $u$, a \textit{robust} method will return a solution $u_h$ such that
\[
\|u-u_h\|_U \lesssim  \inf_{w_h\in U}\|u-w_h\|_U
\]
where $\|\cdot \|_U$ is some norm and $\lesssim$ is a bound by a constant, both of which are independent of  $\epsilon$.

We expect a similar bound to hold under the quasi-optimal norm; however, it is not clear what to expect for other choices of test norms on $V$.  In particular, it is not clear whether it is possible to achieve a completely robust bound under alternative norms, especially ones that generate easily approximated test functions.

@@

\section{Strategy for estimating the DPG energy norm}

The main goal of this paper is to derive a test norm that \textit{does not induce boundary layers in the optimal test functions}, but still induces an energy norm \textit{that does not lose robustness as $\epsilon \rightarrow 0$}.  
%The first condition is satisfied by first decoupling norms on $\left(\tau,v\right)$ such that
%\[
%\left\|\left(\tau,v\right)\right\|_V = \|\tau\|_{H({\rm div},\Omega_h)} +  \|v\|_{H^1(\Omega_h)}.
%\]
%where $\|\tau\|_{H({\rm div},\Omega_h)}$ and $ \|v\|_{H^1(\Omega_h)}$ are both constructed as the sum of norm and seminorms on each respective space.  Ensuring that each seminorm/normed term is of the same order will allow for smooth solutions (under some assumptions on $\beta$).  
The avoidance of boundary layers in the test norm will be described in more detail in the section detailing numerical experiments.

Instead, the goal of this paper will to be derive $\epsilon$-explicit bounds on the finite element error by the best approximation error, and to characterize the dependence of such bounds upon the test norm.  We seek to derive an estimate
\[
\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2}
\]
where both $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ are characterized using
\[
\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,i} \coloneqq C_1^i\|u\| + C_2^i\|\sigma\| + C_3^i\|\widehat{u}\| + C_4^i\|\widehat{f}_n\|,\quad i = 1,2
\]
As it may not be possible to derive $O(1)$ constants for each $C_j^i$, we will aim instead for a quasi-robust estimate, where some constants are allowed to depend on $\epsilon$.  \textcolor{red}{Not sure if I need this sentence here.}

To derive the above $\epsilon$-explicit bounds on the finite element error in norm $U,1$ by the best approximation error in norm $U,2$, we need to show that the DPG energy norm (in which our finite element solution is optimal), is bounded from above and below 
\[
\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim  \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2}.
\]
Our goal is to explicitly derive the constants $C^1_1,\ldots C^1_4$ and $C^2_1,\ldots C^2_4$ that define the norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ respectively, taking into account any dependence of such $C^i_j$ on $\epsilon$.  Our strategy for doing so is broken down into three parts.

@@

A second, weaker result is an upper bound on the energy norm
\[
\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-\left(u_h,\sigma_h,\widehat{u}_h,\widehat{f}_{n,h}\right)\right\|_{E} \lesssim \inf_{w\in U_h}\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-w_h\right\|_{U,2}
\]
where $\|\cdot \|_{U,2}$ is defined as
\[
\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U,2}^2 \coloneqq \|u\|^2 + \frac{1}{\sqrt{\epsilon}}\left(\|\sigma\|^2 + \|\widehat{u}\|^2+ \|\widehat{f}_n\|^2\right).
\]
While the second bound is robust, we have derived such a bound only by explicitly accounting for a factor of $\epsilon^{-1/2}$ in the bounding norm $\|\cdot \|_{U,2}$.  This implies that for very small $\epsilon$, the $L^2$ error may be much smaller than the energy error (in this sense, DPG may lose some efficiency for small $\epsilon$). However, numerical experiments demonstrate much better results, and suggest that, at least for our example problems, $\|u-u_h\|_E \sim \|u-u_h\|_{U}$, implying that the induced energy norm may be equivalent to a norm on the group variable $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)$ that does not grow with $\epsilon$.
